\LaTeX\ Author Guidelines for ICCV Proceedings

### 2020-02-17 chapters/0_abstract.tex
Last updates before submission

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a novel theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied. An extensive comparison is performed to evaluate properties of the clustering algorithms in the context of instance segmentation in images, including robustness to noise and efficiency. We show how one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset. 
\end{abstract}

>>>>

% !TEX root = ../agglo_clust_review.tex
%%%%%%%%% ABSTRACT
\begin{abstract}
We propose a new theoretical framework that generalizes algorithms for hierarchical agglomerative clustering to weighted graphs with both attractive and repulsive interactions between the nodes. This framework defines GASP, a Generalized Algorithm for Signed graph Partitioning, and allows us to explore many combinations of different linkage criteria and cannot-link constraints. We prove the equivalence of existing clustering methods to some of those combinations, and introduce new algorithms for combinations which have not been studied before. 
On stochastic block model problems, GASP compares favorably to spectral clustering. More importantly, we conduct a systematic comparison of various instantiations of GASP in image instance segmentation problems, in terms of accuracy but also efficiency and robustness to noise. 
We find that one of the new algorithms proposed in our framework outperforms all previously known agglomerative methods for signed graphs, both on the competitive CREMI 2016 EM segmentation benchmark and on the CityScapes dataset.
\end{abstract}

### 2020-02-17 chapters/1_intro.tex
Update Fig 1
Last updates before submission

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to such tasks as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods are parameter-based and require users to specify the desired numbers of clusters or a termination criterion (e.g. spectral clustering or iterated normalized cuts) or even to add a seed for each object  (e.g. seeded watershed or random walker).

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to perform the clustering without defining additional parameters. This can be done optimally by solving the so-called \emph{multicut optimization} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. This problem is NP-hard, but approximate solvers have already been proposed \cite{beier2016efficient}. Besides, the general problem of graph partitioning can be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}.

Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient. Despite the fact that there exists a variety of these algorithms, no overarching study has so far been made to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.

In this paper, we propose a novel theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored yet.

We evaluate and compare these algorithms on \emph{instance segmentation} - a computer vision task of assigning each pixel of an image to an object instance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig. \ref{fig:intro_figure}).

\begin{figure*}[t]
\centering
\includegraphics[width=0.9\textwidth]{figs/intro_image_v3.pdf} % left bottom right top
\caption{ Pipeline description: \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure*}

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we evaluate the properties of the algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms the previously known agglomeration methods expressed in the framework. \TODO{Update CS and spectral clustering} 
It also achieves competitive performance on the challenging CREMI 2016 segmentation benchmark and represents the best-performing proposal-free method on CityScapes.
% Our code is available at \url{https://github.com/abailoni/GASP}.

>>>>

\section{Introduction}
In computer vision, the partitioning of weighted graphs has been successfully applied to tasks as diverse as image segmentation, object tracking and pose estimation. 
Most graph clustering methods work with positive edge weights only, which can be interpreted as similarities or distances between the nodes. These methods require users to specify the desired numbers of clusters (as in spectral clustering) or a termination criterion (e.g.\ in iterated normalized cuts) or even to add a seed for each object  (e.g.\ seeded watershed or random walker).

Other graph clustering methods work with so-called \emph{signed graphs}, which include both positive and negative edge weights corresponding to attraction and repulsion between nodes. The advantage of signed graphs over positive-weighted graphs is that balancing attraction and repulsion allows us to obtain a clustering without defining additional parameters. A canonical formulation of the signed graph partitioning problem is the \emph{multicut} or \emph{correlation clustering} problem \cite{kappes2011globally,chopra1991multiway}. This problem is NP-hard, though many approximate solvers have been proposed \cite{lange2018combinatorial,pape2017solving,beier2016efficient,yarkony2012fast}. The general problem of graph partitioning can also be solved approximately by greedy agglomerative clustering \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}. 
Agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter-free and efficient. Despite the fact that a variety of these algorithms exist, no overarching study has so far been conducted to compare their robustness and efficiency or to provide guidelines for matching an algorithm to the partitioning problem at hand.

In this paper, we propose a new theoretical framework that generalizes over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}. 
We then formally prove that some of the combinations correspond to existing clustering algorithms and introduce new algorithms for combinations which have not been explored before.

We evaluate and compare these algorithms on \emph{instance segmentation} -- a computer vision task of assigning each pixel of an image to an object instance. 
We use a CNN to predict the edge weights of a graph such that each node represents a pixel of the image, similarly to \cite{liu2018affinity,lee2017superhuman,wolf2018mutex}, and provide these weights as input to the algorithms in our framework (see Fig.~\ref{fig:intro_figure}).

\begin{figure*}[t]
\centering
\includegraphics[width=\textwidth]{figs/intro_image_v4.pdf} % left bottom right top
\caption{\algname{} example. \textbf{(1)} Raw data from the CREMI 2016 neuron-segmentation challenge. \textbf{(2)} Some short- and long-range predictions of our CNN model, where white pixels represent boundary evidence. \textbf{(3)} Outputs of two agglomerative algorithms included in our proposed generalized clustering framework, with \emph{Sum} and \emph{Average} linkage criteria. The final clustering / instance segmentation is shown in 3a, overlaid with the raw image.  The  agglomeration order in 3b shows which pairs of neighboring pixels were merged first (white), later on (brown/red), or never (black). (\textbf{4}) Some iterations of \algname{} on toy graph examples with attractive/positive (green) and repulsive/negative (red) interactions. At each iteration, the yellow edge with highest interaction is contracted (orange arrows), until only negative edges are left in the graph.
\label{fig:intro_figure}}
\end{figure*}

With our comparison experiments, performed both on 2D urban scenes from the CityScapes dataset and 3D electron microscopy image volumes of neurons, we benchmark all algorithms in our framework, focusing on their efficiency, robustness and tendency to over- or under-cluster.
We show that one of the new algorithms derived from our framework, based on an average linkage criterion, outperforms all previously known agglomeration methods expressed in the framework and that
it achieves competitive performance on CityScapes and the challenging CREMI 2016 segmentation benchmark.

In Sec.~\ref{sec:spectral_clust}, we also show how \algname{} outperforms spectral clustering methods on the task of neuron segmentation and how on synthetic graphs it achieves similar scores to a recently proposed spectral method for signed graphs.

% Our code is available at \url{https://github.com/abailoni/GASP}.

### 2020-02-17 chapters/2_rel_work.tex
Last updates before submission

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation, 
% SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
% whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}. % kulikov2018instance
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, the model generates the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{Gao_2019_ICCV,liu2018affinity,xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, while 
flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. Recently, there has been a growing interest for such  methods that do not involve object detection, since, in certain types of data, object instances cannot be approximated by bounding boxes. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for instance segmentation, 
% SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
whereas a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction. 
% whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{lee2019learning,fathi2017semantic,newell2017associative,de2017semantic}. % kulikov2018instance
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}. 
Other recent successful methods simply let the model predict the relative coordinates of the instance center \cite{neven2019instance,cheng2019panopticdeeplab} or, given a point $(x,y)$ in the image, they train a model to generate the mask of the instance located at $(x,y)$ \cite{sofiiuk2019adaptis}.

\textbf{Edge detection} also experienced recent progress thanks to deep learning, both on natural images \cite{Gao_2019_ICCV,liu2018affinity,xie2015holistically,kokkinos2015pushing} and biological data \cite{lee2017superhuman,schmidt2018cell,meirovitch2016multi,ciresan2012deep}. In neuron segmentation for connectomics, a field of neuroscience we also address in our experiments, boundaries are converted to final instances with subsequent postprocessing and superpixel-merging:
some use loopy graphs \cite{kaynig2015large,krasowski2015improving} or trees \cite{meirovitch2016multi,liu2016sshmt,liu2014modular,funke2015learning,uzunbas2016efficient} to represent the region merging hierarchy; the lifted multicut \cite{beier2017multicut} formulates the problem in a combinatorial framework, whereas 
flood-filling networks \cite{januszewski2018high} and MaskExtend \cite{meirovitch2016multi} use a CNN to iteratively grow one region/neuron at the time; recently, the work of \cite{meirovitch2019cross} made the process more efficient by employing a combinatorial encoding of the segmentation.
A structured learning approach was also proposed in \cite{funke2018large,turaga2009maximin}.

### 2020-02-17 chapters/3_algorithm.tex
Small typos and changes
Last updates before submission

In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm. \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters. The algorithm has two variants. The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

In the second variant (option \emph{addCannotLinkConstraints} is \texttt{True}), Algorithm \ref{main_alg} also introduces cannot-link constraints, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig. \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps. If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained. 
The algorithm terminates when all the remaining clusters are constrained.

@@

\begin{algorithm}[t]
  \begin{flushleft}
  \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
  \footnotesize
  % \small
      \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
      \State Init. interactions between clusters with $\cost_e = w^+_e - w^-_e$
      \Repeat
        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$.
          \State Update interactions \& constraints with neighboring clusters.
        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
          \State Add CannotLink Constraint between $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
      \State
      \Return $\Pi$
  \end{algorithmic}
    \label{main_alg}
  \end{flushleft}

@@

Our main contribution is the generalized algorithm for signed graph partitioning, short GASP, that encompasses several known and novel agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.

@@

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criteria by populating a histogram for each inter-cluster interaction. In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

@@

        \end{tabular}
    \end{subtable} 
    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning \algname{}, given a linkage criterium, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

\begin{figure*}
\centering
\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. The main \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

>>>>

In Algorithm \ref{main_alg}, we provide simplified pseudo-code for the proposed \algname{} algorithm. \algname{} implements a bottom-up approach that starts by assigning each node to its own cluster and then iteratively merges pairs of adjacent clusters. The algorithm has two variants. The first one (option \emph{addCannotLinkConstraints} is \texttt{False}) starts by merging clusters with the strongest attractive interaction and stops once the remaining clusters share only mutual repulsive interactions (see iterations on toy graphs in block 4 of Fig.\ \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}}). After each merging iteration, the interaction between the merged cluster and its neighbors is updated according to one of the linkage criteria $\interact(S_u, S_v)$ listed in Table \ref{tab:linkage-criteria}.

In the second variant (option \emph{addCannotLinkConstraints} is \texttt{True}), Algorithm \ref{main_alg} also introduces cannot-link constraints, which represent mutual exclusion relationships between pairs of nodes that cannot be associated with the same cluster in the final clustering. This variant 
selects the pair of clusters with the highest absolute interaction $|\interact(S_u, S_v)|$, so that the most attractive and the most repulsive pairs are analyzed first (see example in Fig.\ \ref{subfig:with_constraints}). If the interaction is repulsive, then the two clusters are constrained and its members can never merge in subsequent steps. If the interaction is attractive, then the clusters are merged, provided that they were not previously constrained. 
The algorithm terminates when all the remaining clusters are constrained.

@@

\begin{algorithm}[t]
  \begin{flushleft}
  \caption{\algname{}: generalized algorithm for signed graph partitioning}
   \hspace*{\algorithmicindent} \textbf{Input:} Graph $\mathcal{G}(V,E,w^+,w^-)$; linkage criterion $\interact{}$; boolean {\color{blue}addCannotLinkConstraints}  \\
  \hspace*{\algorithmicindent} \textbf{Output:} Final clustering $\Pi$\\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
  \footnotesize
  % \small
      \State Initial clustering: $\Pi=\{\{v_1\}, \ldots, \{v_{|V|}\}\}$
      \State Initialize interactions between clusters with $\cost_e = w^+_e - w^-_e$
      \Repeat
        \State Get $S_u,S_v\in\Pi$ with highest interaction $|\interact{}(S_u,S_v)|$
        \If{\big[{\color{ForestGreen}\textbf{$\interact{}(S_u,S_v) > 0$}}\big] \textbf{and} \big[$S_u,S_v$ \textbf{not} constrained\big]}
          \State Merge cluster $S_u$ with $S_v$
          \State Update interactions \& constraints with neighboring clusters
        \ElsIf{{\color{blue}addCannotLinkConstr} \textbf{and}  \big[{\color{red}\textbf{$\interact{}(S_u,S_v) \leq 0$}}\big]}
          \State Add CannotLink Constraint between $S_u$ and $S_v$
        \EndIf
      \Until{\big[all interactions between clusters are repulsive\big] \textbf{or} \break\hspace*{2.5em} \big[all adjacent clusters have cannot-link constraints\big]}
      \State
      \Return $\Pi$
  \end{algorithmic}
    \label{main_alg}
  \end{flushleft}

@@

Our main contribution is the generalized algorithm for signed graph partitioning, GASP, that encompasses several known and new agglomerative algorithms on display in Table \ref{tab:linkage-criteria}.
In our framework, individual algorithms are differentiated by the linkage criterion employed. We review them in the following paragraphs.

@@

Apart from the linkage criteria defined in Table \ref{tab:linkage-criteria}, additional ones were proposed in the literature:
\cite{nunez2013machine} for example uses a learned approach where a random forest classifier updates the cluster interactions depending on predefined edge and node features; other approaches introduce a weight regularization depending on the size of the clusters \cite{felzenszwalb2004efficient,kardoostsolving}, whereas 
\cite{funke2018large} uses a \emph{quantile} linkage criterion by populating a histogram for each inter-cluster interaction. In our experiments, we decided to focus on the linkage criteria listed in Table \ref{tab:linkage-criteria}, since they represent the most common options.

@@

        \end{tabular}
    \end{subtable} 
    \caption{Existing and new clustering algorithms that can be reformulated as special cases of the proposed generalized algorithm for signed graph partitioning, \algname{}, given a linkage criterion, a type of graph (signed or unsigned) and the optional use of cannot-link constraints. The set $E_{uv}$ is defined as the set of all edges connecting cluster $S_u$ to cluster $S_v$, i.e. $E_{uv}=(S_u \times S_{v \neq u}) \cap E$.}
    \label{tab:linkage-criteria}
\end{table*}

\begin{figure*}
\centering
\includegraphics[width=0.96\textwidth]{./figs/comparison_new.pdf} % left bottom right top
\caption{Failure cases of \algname{} with different linkage criteria highlighted on some difficult parts of the CREMI Challenge data. Only the \emph{wrongly} segmented regions are highlighted in different warm colors. Note that the data is 3D, hence the same color could be assigned to parts of segments that appear disconnected in 2D.  Red arrows point to wrongly split regions. Yellow arrows point out merge errors. The \emph{Average} linkage without cannot-link constraints returned the best segmentation.
\label{fig:cremi_comparison}}
\end{figure*}

### 2020-02-17 chapters/5_experiments_cityscapes.tex
Last updates before submission

\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
We also evaluate the performances of \algname{} on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images.
Several of the current top instance segmentation methods on cityscapes predict affinities, e.g. SSAP \cite{Gao_2019_ICCV} and GMIS \cite{liu2018affinity}. 
Since \cite{liu2018affinity} made the code and model publicly available, we used their pipeline consisting of two CNNs with similar architectures (one predicting semantic scores and the other pixel affinities between instances) and applied all the post-processing methods proposed by them, e.g. excluding background and resizing regions of interest. We then provided the output instance-affinities of the model as input to \algname{}. 
In \cite{liu2018affinity} the instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how strong short-range boundary evidence was never predicted by the model. In Appendix \ref{sec:appendix_cityscapes} we present how we solved this problem by fine-tuning the model with \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}. Finally, the semantic categories were assigned to each instance by a majority vote based on the semantic output.

>>>>

\section{Experiments on CityScapes}\label{sec:cityscapes_exp}
The segmentation performance of \algname{} is evaluated on the CityScapes dataset \cite{cordts2016cityscapes}, which consists of 5000 street-scene images.
Several of the current top instance segmentation methods on cityscapes predict affinities, e.g. SSAP \cite{Gao_2019_ICCV} and GMIS \cite{liu2018affinity}. 
Since \cite{liu2018affinity} made the code and model publicly available, we used their pipeline consisting of two CNNs with similar architectures (one predicting semantic scores and the other pixel affinities between instances) and applied all the post-processing methods proposed by them, e.g. excluding background and resizing regions of interest. We then provided the output instance-affinities of the model as input to \algname{}. 
In \cite{liu2018affinity} the instance-branch of the model was trained with a Binary Cross-Entropy loss, but we noticed how strong short-range boundary evidence was never predicted by the model. In Appendix \ref{sec:appendix_cityscapes} we present how we solved this problem by fine-tuning the model with \emph{S\o resen-Dice} loss, similarly to \cite{wolf2018mutex}. Finally, the semantic categories were assigned to each instance by a majority vote based on the semantic output.

### 2020-02-17 chapters/5_experiments_compare_rules.tex
Last updates before submission

    \captionof{table}{Results on CityScapes test. Methods marked with~$\dagger$ are \emph{proposal-based}. Only methods that do not use external training data (e.g. MS COCO) are shown.}\label{tab:results_cityscapes}

@@

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which present publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.

>>>>

    \captionof{table}{Results on CityScapes test. Methods marked with~$\dagger$ are \emph{proposal-based}. Only methods that do not use external training data (such as MS COCO) are shown.}\label{tab:results_cityscapes}

@@

\subsection{Data: CREMI challenge} \label{sec:cremi_challenge}
We evaluate all algorithms in the proposed framework on the competitive CREMI 2016 EM Segmentation Challenge \cite{cremiChallenge} that is currently the neuron segmentation challenge with the largest amount of training data available. The dataset comes from serial section EM of \emph{Drosophila} fruit-fly tissue and consists of 6 volumes of 1250x1250x125 voxels at resolution 4x4x40nm, three of which come with publicly available training ground truth. The results submitted to the leaderboard are evaluated using the CREMI score, based on the Adapted Rand-Score (Rand-Score) and the Variation of Information Score \cite{arganda2015crowdsourcing}. In Appendix \ref{sec:cremi_details}, we provide more details about the training of our CNN model, inspired by work of \cite{lee2017superhuman,funke2018large}.
